
\section{Discussion}

When performing the regression we map marker positions to a
certain number of components. We experimented with a smaller 
number of components would produce a better
reconstruction of the joint angle data. We found that mapping
to the full amount of components (54) produces the smallest
average error,
we can map up to 35 components with very little degradation
from a full component set.\\

%Because mapping to a full set of components produces the smallest
%average error, 
We also tested using our locally-weighted
regression model to map marker positions directly to joint angles
represented as Euler angles. The average joint angle error per
frame was very high. This can easily be seen in the animations
produced by the reconstructed joint angles. The hand does not
reach the majority of the poses in the motion. From this we see
that there is a clear benefit to using and producing principle
components to reconstruct the joint angles of the hand over 
mapping directly to joint angles.\\

We also experimented with
 three has a larger average error than the marker
set of six, but still appears to produce reasonable results. We
can see this when looking at the top principle components of the
reconstructed motion and comparing it to the top principle 
components of the original motion. For one sequence of motion,
(in Figure BLAH), the top three components for both the original
motion and the reconstructed motion with 3 markers appear to follow
very similar patterns. Although there is information lost in the
reconstruction, the general pattern of motion is the same.\\

Lastly, we attempt to reconstruct motions that are not sign language
using our alphabet database. The motions include counting and general
gesticulations. While the general poses in the 
sequences appear to be reached, the accuracy of the joint angles
is visibly not as good the sign language reconstructions. It
may be necessary to have a different database to properly reconstruct
these motions.\\