
\section{Sparse Marker Selection}
Our method for constructing the sparse marker set exploits the full recordings
that appear in the reference database.  That is, because these recordings 
include a full suite of markers, we can evaluate the value of each marker
in contributing to the whole-hand motion.  A similar approach is described
by Kang et al~\cite{Kang12} but our technique utilizes PCA to compute the markers
directly, as opposed to the exhaustive search proposed by Kang and his
colleagues..

In particular, we conduct PCA over the reference database and, in this case,
PCA is performed with the Cartesian positions of the markers relative
to the root link.  With 13 markers, this leads to a PCA of 39 dimensions.  
In general, PCA produces a covariance matrix and the eigenvectors of this matrix 
create a list of components ordered from most important
to least important.  
%
Each component has 39 coefficients that dictate the influence of each 
marker on that component.  By adding up the contribution of each marker
to all of the components, we can rank-order the influence of the markers on the
full-set of components.  Further, from the eigenvalues, we are given the relative importance
of each principle component with respect to each other.  We can use this importance
as a weighting to bias the components.  Thus, by summing the weighted contribution
of each marker to each of the components, our marker rank ordering can account
for the described bias.

%The marker coeffients are weighted depending 
%on how much the current component contributes to the final PCA reconstruction
%of the database and then summed. Markers with the highest sums are selected to
%be the sparse marker set.

In our results we highlight sparse marker sets of three 
and six markers.
Given the number of markers desired for the sparse set, we select the
set simply as the top markers based the rank-ordering.  We experimented with two methods of
producing this rank-ordering, one with the eigenvalues acting as a weighting bias
and the second treating all of the top-$N$ principle components as equally important and simply
ignoring the remaining components.  Conservatively experimenting with $N$ to be 
between one fourth and three fourths of the full dimensionality, these two approaches 
produced similar results.   However, if we selected $N$ to be the value of the full dimensionality,
we did see reduced quality solutions.  In practice, we employ the eigenvalue weighted ranking for
all results showcased in this paper.  

A nice feature of selecting the marker set in this fashion is that the rank-ordering
simply adds subsequent markers from smaller sets to produce the larger sets.  Thus, the described 
priority ranking reveals which are the definitively \emph{most} influential markers regardless of the
size of the sparse marker set. And so, in practice, adding more
markers for higher quality recordings does not require a complete change of markers, only the
addition of the desired number of markers to the ones employed in the lower quality recording.


%upon the respective marker's contribution to the PCA 
%reconstruction of the reference database.






